### 2023-05-24 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

The electroplating system is an unstable system that relies on multiple parameters being within their respective optimal ranges to achieve a desired mode. 
Several tips can help reduce noise and stabilize the system, such as avoiding the use of an oscilloscope with the charger to avoid power line noise. 
Mechanical noise in the pumping machine can be minimized by using a syringe pump tilted with a bubble inside. 
External electrical noise can be picked up by antennas or connections in the circuit. 
To stabilize internal humidity, turn on the gas pipeline with air into the chamber.

@@

\section{Setup Validation}
\label{sec:setup_validation}

It is recommended to do initial tests in order to verify the setup assembly and the automation routine integration. 
This is an important step to understand in practice how electrospray works.
Factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
Also, liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permittivity. 
And also physical variables such as flow rate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.

\section{Oscilloscope Impedance}
\label{sec:osc_impedance}

The current being measured by the Oscilloscope use its internal impedance. 
The \emph{TiePie} oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
Selecting one or other will multiply or divide your current measurement by 2. 
By default, it is being used 2Mohm differential input, however it was noticed that using the 1Mohm resistance might reduce noise. 
A proposal is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

>>>>

The electroplating system is an unstable system that relies on multiple parameters being within their respective optimal ranges to achieve a desired mode. 
Several tips can help reduce noise and stabilize the system, such as avoiding the use of an oscilloscope with the charger to reduce power line noise. 
Mechanical noise in the pumping machine can be minimized by using a syringe pump tilted with a bubble inside. 
External electrical noise can be picked up by antennas or connections in the circuit. 
And gas pipeline with air into the chamber can be used to stabilize internal humidity and temperature.

@@

### 2023-05-24 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

To continue, a proposal is to prioritize the improvement of the classification step. 
Ideally using machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
By achieving a reliable classification, a more effective controller logic or approaches can be implemented. 
In this regard, a concept of a fuzzy controller will be presented as a potential solution.

@@

        One challenge in implementing the controller in this project is that it does not have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
        As this project involves logical control, it requires a different approach.

@@

        Firstly, the fuzzyfication and defuzzyfication machines were implemented using the data acquired in the experiment of step routine\ref{subsec:step_routine}, mapping the area of each spraying mode according to its potential.
        Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication within the input and output of the controller.

@@

        The controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to the rules listed below.

@@

        The works presented in this report represent a continuation and refinement of previous efforts to develop a more precise and versatile automation routine that can be effectively applied in both industrial and research applications.

>>>>

To continue, a proposal is to prioritize the improvement of the classification step. 
Ideally, using machine learning or another classification algorithm to improve accuracy with a broad range of liquids.
By achieving a reliable classification, a more effective controller logic can be implemented. 
In this regard, a concept of a fuzzy controller will be presented as a potential solution.

@@

        One challenge in implementing the controller in this project is that it does not have a real value as feedback. Instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
        As this project involves logical control, it requires a different approach.

@@

        Firstly, the fuzzyfication and defuzzyfication machines were implemented using the data acquired in the experiment of step routine \ref{subsec:step_routine}, mapping the area of each spraying mode according to its potential.
        Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication within the input and output of the controller.

@@

        The controller is an algorithm that calculates the output with a geometrical calculus on the membership functions of the input and output according to the rules listed below.

@@

        The works presented in this project represent a continuation and refinement of previous efforts to develop a more precise and versatile automation routine that can be effectively applied in both industrial and research applications.

### 2023-05-24 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

This classification by statistical analysis was already implemented in the software library made by the previous student \cite{Monica}.
This method was capable of only classifying dripping, intermittent and cone jet modes. Also in her work, Monica extended the classification to corona or discharge detection.
My contribution was to integrate her work on my control loop model and extend the classification for the multi jet.

To classify the multi jet, after running many steps experiments it was noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range. 
These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.

@@

            \State $spray\_mode \gets "Undefined"$;
            \State $mean \gets sample.mean$; 
            \State $deviation\_mean \gets sample.std\_deviation / sample.mean$;
            \State $mean\_median \gets sample.mean / sample.median$;

            \If{ $mean > 5$}
                \Comment{Sjaak classification \cite{Sjaaks}} 
                \State $spray\_mode \gets "Dripping"$;
                \If{$ 2.5 < mean / std\_deviation < 2.5 \And mean / std\_deviation > 0.3 $}
                \State $spray\_ mode \gets "Intermittent"$;
                \EndIf
            \ElsIf{ $mean / std\_deviation$ < 0.3}
                \State $spray\_ mode \gets "Cone Jet"$;
                \State $cone\_jet\_mean \gets mean$;
            \EndIf

            \If{ $mean / std\_deviation$ > 2.5}
                \Comment{Monica classification \cite{Monica}} 
            \EndIf

            \If{ $spray\_mode == "Cone Jet"$}
                \Comment{João classification} 
                \If{ $cone\_jet\_mean > 1.14 \times mean$}
                    \State $spray\_ mode \gets "Multi Jet"$;
                \EndIf
            \EndIf

@@

    The program developed is capable of running different types of routines and with an easy way to implement new strategies.
    Continuing the methodology, in the setup json file there is a "sequence" attribute which can be chosen between "ramp", "step", "map" or "control".
    The controller thread will manage what the algorithm must do for each sequence.
    Following the control model in Figure\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread.

\subsection{Ramp}

@@

\subsection{Step}
\label{subsec:step_routine}

The step sequence is done by the same command send to the power supply but with the maximum slope value in order to proximate of a step signal.
By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage, as represented in algorithm \ref{alg:stepping_algorithm}.

\begin{algorithm}
    \caption{STEP sequence in controller thread}\label{alg:stepping_algorithm}
    \begin{algorithmic}
    \Procedure{STEP}{$voltage\_start,voltage\_stop$} 
        \State $voltage \gets voltage\_start$
        \While{$voltage \leq voltage\_stop$} \Comment{scanning voltage range}
            \State \Call{send\_voltage\_command}{voltage}
            \State \Call{sleep}{step \_time}
            \State $voltage \gets voltage + step\_size$
        \EndWhile
    \EndProcedure

    \end{algorithmic}
\end{algorithm}

@@

The map was inspired in Gañan-Calvo\cite{gananCalvo} work where he points how liquid conductivity influences the cone jet stability island.

\begin{figure}[H]
    \center
    \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
    \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} . The window formed by these points is where the system operated in the stable cone-jet. Operational windows depend on the liquid and configuration setup. Different windows are represented for different liquid conductivity. The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
    \label{fig:ganan_calvo_fig}
\end{figure}

To reach certain map it is necessary to traverse flow rate and voltage values acquiring samples.
The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
The algorithm for this sequence is a loop of the step sequence\ref{subsec:step_routine} for each flow rate chosen, and it is represented in the algorithm \ref{alg:mapping_algorithm}.

    \begin{algorithm}
        \caption{MAP sequence in controller thread}\label{alg:mapping_algorithm}
        \begin{algorithmic}
        \Procedure{MAP}{$flowrate\_values$} 
            \ForAll{flowrate\_values}  \Comment{scanning in the flowrate range}
                \State \Call{send\_flowrate\_command}{flowrate}
                \State $voltage \gets voltage\_start$
                \While{$voltage \leq voltage\_stop$} \Comment{scanning in the voltage range}
                    \State \Call{send\_voltage\_command}{voltage}
                    \State \Call{sleep}{step \_time}
                    \State $voltage \gets voltage + step\_size$
                \EndWhile
            \EndFor
        \EndProcedure

        \end{algorithmic}
    \end{algorithm}

    In Figure \ref{fig:map2Data_fig} it can be seen the data acquired in this mapping experiments. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
        \caption{Mapping Experiment data collected. The Figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined in the routine.
        The third graph shows the current mean value of each data sample.}
        \label{fig:map2Data_fig}
    \end{figure}

    With all the data collected, classified and saved in real time, further analysis and studies can be done. For example, Figure \ref{fig:map3Data_fig} illustrate the data automatically classified and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that a comparison on automatic results with previous researches can be done, such as showed in Figure \ref{fig:ganan_calvo_fig}, validating the algorithm.

@@

This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve the project goals. 
Next chapter \ref{chap:Results}, it will be discussed the results reached.

>>>>

This classification by statistical analysis was already implemented in the software library made by the previous student \cite{Monica}.
This method was capable of only classifying dripping, intermittent and cone jet modes using the rules defined in figure \ref{fig:statis_ranges}. 
\begin{figure}[H]
    \centering
    \resizebox{150mm}{!}{\includegraphics{Figuras/may/statistical_analysis.png}}
    \caption{Statistical classification modes ranges.}
    \label{fig:statis_ranges}
\end{figure}

Also in her work, Monica extended the classification to corona or discharge detection.
My contribution was to integrate her work on a classic closed loop control model using parallel computing and extend the classification for the multi jet.

To classify the multi jet, after running many steps experiments it was noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range. 
These effects were exposed by Ryan\cite{Ryan}. In his work the relation between current per jet is defined in both cone jet and multi jet modes.

@@

            \State $spray\_mode \gets "Undefined"$;

            \State $spray\_mode$ = \Call{sjaaks\_classification}{$sample$} \Comment{Sjaak classification \cite{Sjaaks}}

            \If{ $mean > 1000$}
            \Comment{Monica classification \cite{Monica}} 
                \State $spray\_mode \gets "Corona"$;
            \EndIf

            \If{ $spray\_mode == "Cone Jet"$}
            \Comment{João classification} 
                \If{ $mean > 1.14  \times cone\_jet\_mean$}
                    \State $spray\_ mode \gets "Multi Jet"$;
                \EndIf
            \EndIf

@@

    The program developed is capable of running different types of routines and with an easy way to implement new strategies.
    Continuing the methodology, in the setup json file there is a "sequence" attribute which can be chosen between "ramp", "step", "map" or "control".
    The controller thread will manage what the algorithm must do for each sequence.
    Following the control model in Figure \ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread.

\subsection{Ramp or Step}
\label{subsec:step_routine}

@@

The step sequence is done by the same command sent to the power supply but with the maximum slope value in order to proximate of a step signal.
By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage.

% \begin{algorithm}
%     \caption{STEP sequence in controller thread}\label{alg:stepping_algorithm}
%     \begin{algorithmic}
%     \Procedure{STEP}{$voltage\_start,voltage\_stop$} 
%         \State $voltage \gets voltage\_start$
%         \While{$voltage \leq voltage\_stop$} \Comment{scanning voltage range}
%             \State \Call{send\_voltage\_command}{voltage}
%             \State \Call{sleep}{step \_time}
%             \State $voltage \gets voltage + step\_size$
%         \EndWhile
%     \EndProcedure

%     \end{algorithmic}
% \end{algorithm}

@@

The map was inspired in Gañan-Calvo\cite{gananCalvo} work where he points how liquid conductivity influences the cone jet stability island. 
The window formed by these points is where the system operated in the stable cone-jet. Operational windows depend on the liquid and configuration setup. Different windows are represented for different liquid conductivity. The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.

\begin{figure}[H]
    \center
    \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
    \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} .}
    \label{fig:ganan_calvo_fig}
\end{figure}

    To reach certain map it is necessary to traverse flow rate (X axis) and voltage (Y axis) values acquiring samples.
    In Figure \ref{fig:map2Data_fig} it can be seen how the mapping procedure works. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.

    \begin{figure}[H]
        \center
        \includegraphics[width=16cm]{Figuras/report2/map2Data.png}
        \caption{Mapping Experiment data collected. The Figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined in the routine.
        The third graph shows the current mean value of each data sample.}
        \label{fig:map2Data_fig}
    \end{figure}

    With all the data collected, classified and saved in real time, further analysis and studies can be done. 
    For example, Figure \ref{fig:map3Data_fig} illustrates the data automatically classified and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that a comparison between manual and automatic results can be done, validating the algorithm, as will be shown in section \ref{subsec:map_results}.

@@

This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve the project goals. 
Next chapter \ref{chap:Results}, the results reached will be discussed.

### 2023-05-24 Documentation/UFMG/PFCII/Results/Results.tex
documentation

The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. 
With the save data by streaming in saving thread, it was achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.

Also, most power supplies rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person and takes some time to achieve the desired voltage.
Moreover, the electrospray phenomena has a known hysteresis, that can be seen in figure \ref{fig:ganan_calvo_fig}, and can perform different results depending on the previous electric potential.
Running a computer routine that automatically sends commands to the power supply and pump machine allowed obtaining faster and more reliable experiment data points.

@@

The classification results in the algorithm implemented as described in section \ref{sec:section_classification} showed good accuracy for all the classifications described in section \ref{sec:spraying_modes_subsec}.
Nevertheless, the multi jet classification made by a current value factor of 1.14 above the cone jet is just effective for pure ethanol, liquid used in all this project.

Even if the multi jet classification just works for pure ethanol, the data saved with correct classification in ethanol can be used to extract any other signal information about the multi jet or to train a black box classification algorithm.

@@

The first classification results were made exploring the voltage ranges. 
For that, a flow rate was fixed to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
The figure \ref{fig:step_class} shows three graphs.

The first shows the controller output signal as an input voltage of the process. As it is a step routine, an increasing voltage with steps of sizes 50V and time between each step of 5 seconds was implemented. The voltage range is between 3k-10k Volts.

@@

For example, dripping mode has a current mean of 0V. The Intermittent state has a high variation of values that can be seen by the increased thickness on the graph. The cone jet is a thinner graph because of its constant signal. Multi Jet  has the same shape as cone jet but with a higher mean value. Corona sparks are not showed in the graph because its discharges has a high current value above the axis limits.

@@

For validation with literature and also to expose the benefits of the automated routine and classification, the map sequence proof itself the best result of this work. 
Initially, for better understand pure ethanol classification regions through voltage and flow rate ranges, it was made a manual map seen in figure \ref{fig:stability_1}.

@@

    In order to validate the automatic classification, experiments were made comparing both visual and automatic stability island on the same experiment.
    Figure \ref{fig:stability_2} shows that automatic stable cone jet region could be identified in the same region as visually seen by the high speed camera (data acquired manually).

@@

    With the development of a multi jet classification using the logic explained in section \ref{sec:section_classification}, the same experiment was repeated, as shown in Figure \ref{fig:stability_6}.

@@

    \subsubsection{Non-dimensional axis}

    To have a better comparison with literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands showed in figure \ref{fig:ganan_calvo_fig}, with a visual juxtaposition of the shapes, the data displayed in Figure \ref{fig:stability_8} using the non-dimensional numbers used in his work\cite{gananCalvo}.

@@

    The results of mapping experiment corresponded visual, literature and automatic regions of classification, giving authentication to the method.

@@

    The results of the classification process were favorable for experiment automation, however, the inaccuracy of the classification by statistical methods, specially the Multi Jet\ref{subsec:Multi Jet}, limited the development of a complete control project.
    Together with the amount of variables that need to be syntonized makes it hard to stabilize in a desired mode.
    Even with all those problems, a simple controller project could be implemented, as described in section \ref{sec:control_model}, that validated the efforts of remodeling all software into a closed loop control model.

    The controller not only stabilized in cone jet mode, but also could reject perturbation, as seen in Figure \ref{fig:control_results}, where the flow rate was manually changed.
    First graph shows current acquired. It starts as intermittent state, with an oscillating signal. This can be validated with the blue colored sample on the third graph representing its automatic classification. 
    The second graph shows the controller actuating increasing the voltage to achieve a stable cone jet mode.
    After a period of time in cone jet, a manual increase in the flow rate was done, serving as a perturbation of the system, and it can be seen that the effect of that was to return to intermittent state with the oscillating signal. The controller again, actuate increasing the voltage to reach the cone jet stability island. 
    This procedure was repeated after some seconds of stabilization in cone jet, increasing once more the flow rate manually, and again the system automatically adjusting the voltage.
        \begin{figure}[H]
            \center
            \includegraphics[width=16cm]{Figuras/19:03/control_first_results.png}
            \caption{Simple controller validation experiment. For this experiment, after waiting the system to stabilize in the desired spraying mode it was made a perturbation test changing the flow rate. The classification legend follows the same color reference in all project.}
            \label{fig:control_results}
        \end{figure}

    After 200s of experiment the system had some breaks up of the cone jet into a droplet and stabilized again. This is represented by the peak values in current signal. The classification correctly identified as intermittent, seen as blue dots in the third graph, and the controller reacted increasing the voltage, in a situation that can be considered as noise. A filter can be applied in a more complex controller project to avoid this.

>>>>

The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. 
It was achieved less program memory during the experiment and, specially, safety for not losing data in case the program fail during an experiment with the usage of json streams in the saving thread.

Also, most power supplies rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person, and it takes some time to achieve the desired voltage.
Moreover, the electrospray phenomena has a known hysteresis, that can be seen in figure \ref{fig:ganan_calvo_fig}, and can perform different results depending on the previous electric potential.
Running a computer routine that automatically sends commands to the power supply and pump machine allowed obtaining faster and more reliable experiment data points.

@@

The classification results in the algorithm implemented as described in section \ref{sec:section_classification} showed high accuracy for all the classifications described in section \ref{sec:spraying_modes_subsec}.
Nevertheless, the multi jet classification made by a current value factor of 1.14 above the cone jet is just effective for pure ethanol, liquid used in all this project.

Even if the multi jet classification just works for pure ethanol, the data saved with correct classification for ethanol can be used to extract any other signal information about the multi jet or to train a black box classification algorithm.

@@

The first classification results were made exploring the voltage ranges. 
For that the setup file was configured to run a step routine with a fixed flow rate of 0.7 uL/min., as defined in \ref{subsec:step_routine}.

The figure \ref{fig:step_class} shows three graphs. 
The first is about the controller output signal as an input voltage of the process. As it is a step routine, an increasing voltage with steps sizes of 50V and time between each step of 5 seconds was implemented. The voltage range is between 3k-10k Volts.

@@

For example, dripping mode has a current mean of 0V. The Intermittent state have a high variation of values that can be seen by the increased thickness on the graph. The cone jet is a thinner graph because of its constant signal. Multi Jet  has the same shape as cone jet but with a higher mean value. Corona sparks are not showed in the graph because its discharges has a high current value above the axis limits.

@@

For validation with literature and also to expose the benefits of the automated routine and classification, the map sequence proof itself the best result of this work. 
Initially, for better understanding of pure ethanol classification regions through voltage and flow rate ranges, a manual map was made, as seen in figure \ref{fig:stability_1}.

@@

    In order to validate the automatic classification, experiments were made comparing both visual and automatic stability island on the same experiment.
    figure \ref{fig:stability_2} shows that automatic stable cone jet region could be identified in the same region as visually seen by the high speed camera (data acquired manually).

@@

    With the development of a multi jet classification using the logic explained in section \ref{sec:section_classification}, the same experiment was repeated, as shown in figure \ref{fig:stability_6}.

@@

    For a better comparison with literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands shapes showed in figure \ref{fig:ganan_calvo_fig}, a visual juxtaposition of the same data in figure \ref{fig:stability_6} was displayed in figure \ref{fig:stability_8} using the non-dimensional numbers of potential and flow rate on the axis.

@@

        The holes of data in figure \ref{fig:stability_8} is because of the logarithmic scale in the x-axis. 
        To fill the graph and compare with literature the behavior of the cone jet island while increasing the conductivity, other 3 experiments with different conductivities solutions of ethanol were done with help of a PhD in chemical engineering, L. P. Di Bonito.
        Each graph in figure \ref{fig:conductivity_test} took around 5 hours of experiment and 20 GB of data stored.

        While increasing conductivity, the cone jet stability region changes its shape and slightly moves to the right, as demonstrated by Gañán-Calvo in figure \ref{fig:ganan_calvo_fig}.
        The multi jet classification was not considered in these experiments and were classified as 'Undefined' because the classification rule defined in this project works just for pure ethanol.

        \begin{figure}[H]
            \center
            \includegraphics[width=18cm]{Figuras/may/conductivity_test.png}
            \caption{Mapping experiment for different conductivities of ethanol solution.}
            \label{fig:conductivity_test}
        \end{figure}

    The results of automatic mapping experiment corresponded manually and with literature the regions of classification, validating the method.

@@

    The results of the classification process were favorable for experiment automation, however, the inaccuracy of the classification by statistical methods, specially the Multi Jet \ref{subsec:Multi Jet}, limited the development of a complete control project.
    Together with the amount of variables that need to be adjusted it is hard to stabilize in a desired mode.
    Even with all those problems, a simple controller project could be implemented, as described in section \ref{sec:control_model}, that validated the efforts of remodeling all software into a closed loop control model.

    The controller not only stabilized in cone jet mode, but also could reject perturbation, as seen in figure \ref{fig:control_results}, where the flow rate was manually changed.
    First graph shows the raw current acquired during this experiment.
    The second graph shows a voltage graph where it can be seen the controller actuating increasing the voltage to achieve a stable cone jet mode.
    The third graph shows the mean value of each sample colored representing its automatic classification.

    At the beginning, the system starts up with initial voltage of 4500 V, being classified as intermittent state, defined by an oscillating signal in first graph and blue samples in third graph. 
    The controller then, automatically actuates increasing the voltage to reach the stable cone jet. 
    After a period of stability, it was done a manual increase in the flow rate, serving as a perturbation of the system, and it can be seen that the effect of that was to return to intermittent state with the oscillating signal. 
    The controller again, actuates by increasing the voltage to reach the cone jet stability island. 
    This procedure was repeated after some seconds of stabilization in cone jet, increasing once more the flow rate manually, and again the system automatically adjusted the voltage.

    \begin{figure}[H]
            \center
            \includegraphics[width=16cm]{Figuras/19:03/control_first_results.png}
            \caption{Simple controller validation with manual perturbations in flow rate.}
            \label{fig:control_results}
        \end{figure}

    After 200 seconds of experiment the system had some breaks up of the cone jet into a droplet and stabilized again, represented by the peak values in current signal. In this case the classification correctly identified as intermittent because of its signal shape, seen as blue dots in the third graph, but the controller reacted increasing the voltage in a situation that can be considered as noise because it was a small period of instability inside the stability region that could be a result of other external perturbation such as a bubble in the liquid line. A filter can be applied in a more complex controller project to avoid this.
